---
title: "Readme: About me"
author: "Max Taylor" 
output:
  md_document:
    variant: gfm # github format
date: "`r format(Sys.time(), '%d %B %Y')`"
---


# Headings: 

You can have headings using the hastags (more hastags mean a smaller font / organization)

## Code chunks

You can include code chunks like these below (note that you can use `echo` to include or exclude the code). See that this chunk is called 'naming-chunk' 
```{r naming-chunk, echo = FALSE}
hist(iris$Sepal.Length)

```
#New YAML Headings
---
title: "Readme: About me"
Author: "Max Taylor"
output:
  md_document:
    variant: gfm # github format
date: June 21, 2025
---

```{r}
#Setting Woriking Directoy
setwd("C:/Users/mtaylor03/Documents/SISRM Assignment 1")
```

```{r}
#Giving histogram new title
hist(iris$Sepal.Width)
```


## Learning more

To learn more about R and your options, you can look at this [RMarkdown guide](https://zsmith27.github.io/rmarkdown_crash-course/lesson-2-rmd-creation.html).


### Notes
You can test out what the 'pretty' version of the file would look like by changing output to have this instead of md_document (and following lines (ignore the `r' portion`))





