---
title: "Assignment 1"
output:
  Author: "Max Taylor"
  md_document:
    variant: gfm # github format
date: "`r format(Sys.time(), '%d %B %Y')`"
---

```{r}
#Setting Working Directory
setwd("C:/Users/mtaylor03/Documents/UChicago SISRM/Assignment 1")
```

```{r}
#Giving histogram new title
hist(iris$Sepal.Width)
```



# Headings: 

You can have headings using the hastags (more hastags mean a smaller font / organization)

## Code chunks

You can include code chunks like these below (note that you can use `echo` to include or exclude the code). See that this chunk is called 'naming-chunk' 
```{r naming-chunk, echo = FALSE}
hist(iris$Sepal.Length)
```

## Learning more

To learn more about R and your options, you can look at this [RMarkdown guide](https://zsmith27.github.io/rmarkdown_crash-course/lesson-2-rmd-creation.html).


### Notes
You can test out what the 'pretty' version of the file would look like by changing output to have this instead of md_document (and following lines (ignore the `r' portion`))

```{r yaml-example-code, eval = FALSE}
output:
  html_document:
    toc: false
    theme: united
    
```
